\plaintitle

### 2018-01-20 paper/main.tex
Added: Einleitung

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{Lock-a-dos: Ein Rucksack mit Selbstschutz}
\def\plainauthor{Alexander Schuhmann, Max ??????, Michael Stadler, Maximilian Pachl}
\def\emptyauthor{}
\def\plainkeywords{Rucksack; Diebstahl; Selbstüberwachung; Smartphone; Sensoren; Wearable}
\def\plaingeneralterms{Dokumentation}

@@

\numberofauthors{4}
\author{%
  \alignauthor{Alexander Schuhmann\\
    \email{e-mail address}}\\
  \alignauthor{Max ??????\\
    \email{e-mail address}}\\
  \alignauthor{Michael Stadler\\
    \email{e-mail address}}\\
  \alignauthor{Maximilian Pachl\\
    \email{pachl@hm.edu}}\\
}

@@

\section{Einleitung}

This format is to be used for submissions that are published in the
conference proceedings. We wish to give this volume a consistent,
high-quality appearance. We therefore ask that authors follow some
simple guidelines. You should format your paper exactly like this
document. The easiest way to do this is to replace the content with
your own material.  This document describes how to prepare your
submissions using \LaTeX.

@@

It is important that you write for the SIGCHI audience. Please read
previous years' proceedings to understand the writing style and
conventions that successful authors have used. It is particularly
important that you state clearly what you have done, not merely what
you plan to do, and explain how your work is different from previously
published work, i.e., the unique contribution that your work makes to
the field. Please consider what the reader will learn from your
submission, and how they will find your work useful. If you write with
these questions in mind, your work is more likely to be successful,
both in being accepted into the conference, and in influencing the
work of our field.

>>>>

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{Lock-a-dos: Ein Rucksack mit Selbstschutz}
\def\plainauthor{Alexander Schuhmann, Maximilian Balluff, Michael Stadler, Maximilian Pachl}
\def\emptyauthor{}
\def\plainkeywords{Rucksack; Diebstahl; Selbstüberwachung; Smartphone; Sensoren; Wearable}
\def\plaingeneralterms{Dokumentation}

@@

\numberofauthors{4}
\author{%
  \alignauthor{Alexander Schuhmann\\
    \email{e-mail address}}\\
  \alignauthor{Maximilian Balluff\\
    \email{e-mail address}}\\
  \alignauthor{Michael Stadler\\
    \email{e-mail address}}\\
  \alignauthor{Maximilian Pachl\\
    \email{pachl@hm.edu}}\\
}

@@

\section{Einleitung}
Manchmal ist es gar nicht so leicht alleine mit seinem Gepäck
unterwegs zu sein. Beispielweise möchte man seine Sachen nicht 
unbeaufsichtigt am Strand zurücklassen, wenn man eine Runde
im Meer schwimmen möchte. Gerade in beliebten Urlaubsregionen
kommt es schnell mal vor, dass man um seinen Geldbeutel 
erleichtert wird. Um diesem Problem vorzubeugen wurde im Rahmen
dieser Arbeit ein Rucksack entwickelt, der durch eine vielzahl
von Sensoren erkennen kann ob sich jemand an dem gesicherten
Rucksack zu schaffen macht. Im Falle eines unberechtigten 
Zugriffes sind mehrere Abwehrmechanismen denkbar:

\begin{itemize} 
\item Lauter Alarm zur Abschreckung
\item SMS an Besitzer mit GPS Position
\item Stromschläge durch einen Taser
\end{itemize}

Zur komfortablen Konfiguration kann der Besitzer mit seinem
Smartphone verschiedene Profile für verschiedene Situationen 
(Bsp.: Weniger Sensoren, wenn auf dem Rücken getragen)
erstellen und aktivieren. Bei der vorliegenden Umsetzung handelt
es sich nur um einen Prototypen der weder auf Kosten, noch auf
Platz optimiert ist.

\section{Platform}

\section{Sensorik}

\subsection{Thermosensor}

\subsection{Beschleunigungssensor}

\subsection{Lichtsensor}

\section{Aktoren}

\subsection{Elektronisches Schloss}

\subsection{Alarm}

@@
